\section{Data Previews and Data Release 1} 
\label{sec:datapreview}

A series of three Data Previews (DP) and one Data Release (DR) are planned:
\begin{itemize}
\item Data Preview 0 (DP0): Based on simulated LSST-like data.
\item Data Preview 1 (DP1): Based on a subset of early science-grade commissioning data taken with LSSTComCam during commissioning.
\item Data Preview 2 (DP2): Based on a full reprocessing of all science-grade data taken with LSSTCam during commissioning.
\item Data Release 1 (DR1): Based on  the first year of LSST data. 
\end{itemize}
Each successive Data Preview will demonstrate increasing levels of functionality and product maturity, progressively building toward the first full Data Release (DR1).
Because the commissioning observation period is relatively short (Section~\ref{ssec:transition}), the Data Previews will necessarily cover smaller areas and shorter timescales than a standard Data Release.

Successive data previews will exercise more and more functionality and products building up towards Data Release 1. 
Due to the relatively short time periods available for commissioning observations (\S~\ref{ssec:transition}), the Data Previews will necessarily be limited in their area and temporal coverage relative to a full Data Release. 

The data products that comprise the Data Previews and Data Releases are produced by the LSST Science Pipelines~\citep{2019ASPC..523..521B,2018PASJ...70S...5B}.
For an introduction to the LSST data products, see~\citet{RubinDataProductsAbridged} and for a detailed description, see the LSST~\dpdd{},~\citedsp{LSE-163}.
Each Data Preview and LSST Data Release will be accompanied by its own release-specific documentation\footnote{For an example, see the online DP0.2 documentation {\url{https://dp0-2.lsst.io/data-products-dp0-2/}}.}, giving e.g. the  database schema for the catalogs included in that dataset.
Table~\ref{tab:data-preview-summary} provides a summary of the expected early science data products available in DP0, DP1, DP2 and the LSST Data Release 1.
Prior to DR1, not all columns described in te DPDD may be prodiced, depending on the quality and volume of the data from commissioning, and the maturity of the science pipelines. 
All LSST data products will be subject to the embargo periods described in~\citeds{DMTN-199}; 30 days during commissioning and 80 hours during operations for pixel data.
\input{tables/rubin_early_dr_scenario}

The following sections outline which data products can be expected in each planned Data Preview and Data Release, and on what timescale.
Table~\ref{tab:ops-timeline} in Section \ref{sec:timeline} provides a combined view of the expected data preview schedule and associated uncertainties.

\subsection{Data Preview 0}
\label{sec:dp0}

Data Preview 0 (DP0) was the first of three Data Previews to be released during the period leading up to the start of Rubin Observatory Operations. 
Data Preview 0 contained three stages, all based on simulated LSST-like data products. 
DP0 was intended to serve as an early integration test of the LSST Science Pipelines and the Rubin Science Platform (RSP), and to enable a limited number of astronomers and students to begin early preparations for science with the LSST.

\subsubsection{Data Preview 0.1}
\label{sec:dp01}

Data Preview 0.1 (DP0.1) was released to a group, approximately 300,  of early adopters from the community in June 2021. 
It is based on simulated LSST-like images generated by the Dark Energy Science Collaboration (DESC) for their Data Challenge 2 (DC2),~\citep{2021ApJS..253...31L}.
DP0.1 used the 300~\sqdeg of DC2 images that were simulated for five years of the LSST’s wide-fast-deep component (WFD) using a baseline cadence,~\citedsp{PSTN-055}.
The DESC processed the simulated DC2 images with~\href{https://pipelines.lsst.io/v/v19_0_0/index.html}{Version 19} of the LSST Science Pipelines, producing calibrated images and catalogs.
DP0.1 made the DESC’s DC2 images and catalogs available to users through an early version of the Rubin Science Platform (RSP) running at the US DAC.
DP0.1 has now been retired from the publicly available RSP instance.

For full details on DP0.1 including an exact description of the data products that were served, see the documentation at \url{https://dp0-1.lsst.io/}.

\subsubsection{Data Preview 0.2}
\label{sec:dp02}

Data Preview 0.2 (DP0.2) was released to approximately 600 early adopters from the community in June 2022, exactly 1 year after DP0.1. 
The input simulated image dataset, DESC's ``DC2,'' used for DP0.2 was the same as that used for DP0.1.
In this case, the Rubin team itself processed the simulated DC2 images with~\href{https://pipelines.lsst.io/v/v23_0_0/index.html}{Version 23} of the LSST Science Pipelines.
DP0.2 makes the Rubin reprocessed DESC DC2 images and catalogs available to users through an early version the Rubin Science Platform (RSP) running at the US DAC. 

For full details on DP0.2 including an exact description of the data products served, see the documentation at \url{https://dp0-2.lsst.io/} .

\subsubsection{Data Preview 0.3}
\label{sec:dp03}

Delivered in June  2023, DP0.3 is the last in the DP0 series of Data Previews based on simulated LSST-like data. 
DP0.3 supports the Solar System Science Collaboration by hosting their simulated 1-year and 10-year Prompt Products Database (PPDB) catalog to enable moving object analysis development in the RSP at the US DAC.
DP0.3 is based on an entirely independent simulation and has no data in common with DP0.2.

For full details on DP0.3 including an exact description of the data products served, see the documentation at \url{https://dp0-3.lsst.io/}

\subsection{Data Preview 1}
\label{ssec:dp1}

Data Preview 1 (DP1) will serve data products generated from a subset of science-grade astronomically useful images  taken  during  the ComCam on-sky commissioning campaign (\S~\ref{ssec:commissioning-comcam}), to enable the community to prepare to work with LSST data. 
The planned release date for DP1 is 30 June 2025. 

Seven target fields observed as part of the ComCam on-sky observing campaign  have been selected as the basis for DP1 due to their quality and scientific usefulness.  
These seven fields, listed in Table~\ref{tab:dp1_fields} together with their central pointing coordinates, span a range of stellar densities, have good overlap with external reference datasets, and span the breadth of the four primary LSST science themes. 
\input{tables/dp1_fields}

Table~\ref{tab:dp1_fields_visits} provides a summary of the band coverage for the  fields  used as a basis for DP1. 
Figure~\ref{fig:dp1_fields_psf_maglim} shows the resulting integrated depth, expressed in terms of the flux of an unresolved source that would be measured with signal-to-noise ratio $S/N = 5$, using the $r$ band as an example.
47 Tuc and Fornax dSph are both dense star fields, and the core of 47 Tuc is saturated in the LSSTComCam commissioning images.
No coadds were produced for these regions during the on-sky commissioning campaign, hence the holes in the center of the figures.
A typical observing epoch on a given target field consisted of 5-20 visits in each of the three loaded filters.
Nearly all the visits  were taken with one single 1x30 second exposure time and not  2x15 second snaps\footnote{At this time, studies as to whether the LSST will use a 1x30 single exposure or 2x15 snaps as the default standard visit are ongoing with LSSTCam data, and a decision will be made prior to starting the LSST. }.
Only 1x30 second exposure images are included in DP1.
\input{tables/dp1_fields_visits}
\input {figures/dp1_fields_depths}

The  processing and preparation of LSSTComCam data for DP1 took place during the first half of 2025. 
The delivered data products for DP1 are presented in Table~\ref{tab:data-preview-summary}.
DP1 included approximately 2000 exposures.
The processing of crowded fields in the centers of 47 Tuc and Fornax was on a best-effort basis.
The center of 47 Tuc is saturated and so no coadd images were  produced for this region.
Solar System catalogs contained observations of known objects from the MPC Orbit Catalog (MPCORB) tables as well as any new discoveries. 
The snapshot of the MPCORB Catalog tables included in DP1 was taken from around the time of DRP processing for DP1. 

Individual exposures taken during the commissioning campaign  that did not meet the quality control standard of being ``science-grade, astronomically useful'' images, were not be included in the DP1 release,  and consequently, the exact number of exposures and coadd depths in DP1 was different to what was seen during the commissioning campaign.
Additionally, some columns were missing from some catalogs due to the small data sets involved in DP1.
There were  no cell-based coadds in DP1, nor \textit{ShearObject} catalog.
Both of these are currently stretch goals for DP2.
		
\subsection{Data Preview 2}
\label{ssec:dp2}

Data Preview 2 (DP2) will serve data products generated from a subset of science-grade astronomically useful images taken during the LSSTComCam on-sky commissioning campaign, \S~\ref{ssec:commissioning-lsstcam},  to enable the community to prepare to work with LSST data. 

During the Early Operations Optimization Phase of Rubin Operations, as the LSST survey begins, the LSSTCam commissioning data (Section~\ref{ssec:commissioning-lsstcam}) will be reprocessed to produce DP2.
Any additional science-grade images acquired before 13 January 2026 {\it that fall within the existing DP2 footprint} may be incorporated into DP2.  
Before this date, any new area observed by the FBS is expected to have very low visit counts. 
To avoid including such sparsely sampled regions in the processing, only data that increases depth within the established footprint will be added.

Table~\ref{tab:data-preview-summary} presents a summary of the data products expected in DP2.
Cell-based coadds remain a stretch goal for DP2.
All data products delivered with DP1 will also be produced and included in DP2.
The DRP Solar System Processing (SSP) is designed to be a Rubin-only product, meaning that it does not begin with the Minor Planet Center (MPC) catalog to identify objects discovered by other observatories, as is done in the Prompt Processing.
Instead, it constructs a self-contained “Rubin-only Solar System orbit catalog,” which, although less complete, can be more rigorously debiased than the catalog produced in Prompt mode.
For DP2, as in DP1, the available data are insufficient to produce a meaningful Rubin-only catalog from orbit associations.
Therefore, Solar System products in DP2 will be generated by positional cross-matching of Rubin difference-image detections (\emph{DiaSources}) with predicted ephemerides of known objects from the MPCORB catalog.

The planned release time range for DP2 is June -- September 2026.

\subsection{Data Release 1}
\label{ssec:dr1}

LSST Data Release 1 will be based on the first year  of data taken as part of the 10-year survey. 
Data Release Processing of this dataset is estimated to take approximately one full year, making the expected delivery date approximately two years following the start of the 10-year survey.
DR1 will be the first Data Release in which all data products, as described in the DPDD \citep{LSE-163} will be provided.
Table~\ref{tab:data-preview-summary} presents a summary of the data products expected in DR1.



