\documentclass[DM,authoryear,lsstdraft,toc]{lsstdoc}
% lsstdoc documentation: https://lsst-texmf.lsst.io/lsstdoc.html
\input{meta}

% Package imports go here.
\usepackage{booktabs}
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{xcolor,color, colortbl}
\usepackage{enumitem} % in preamble


\usepackage{graphicx}
\usepackage{subcaption}

\usepackage{multirow} %for multirow
\usepackage{rotating} %for sideways, rotating "samples" at 90°"

\usepackage{arydshln}
\setlength{\dashlinedash}{.4pt}
\setlength{\dashlinegap}{.8pt}
\usepackage{makecell}
\usepackage{amssymb}

% Colors for timeline
\definecolor{TLOrange0}{HTML}{F26035}
\definecolor{TLOrange2}{HTML}{F58137}
% \definecolor{TLOrange2}{HTML}{FAA21A}
\definecolor{TLOrange3}{HTML}{FBB982 }

% Define the Rubin colors here
\definecolor{RubinLightTeal}{HTML}{00BABC}
\definecolor{RubinDarkTeal}{HTML}{058B8C}
\definecolor{RubinWhite}{HTML}{F5F5F5}
\definecolor{RubinBlack}{HTML}{313333}

% The complimentary teal colors
\definecolor{RubinTeal0}{HTML}{D9F7F6}
\definecolor{RubinTeal1}{HTML}{B1F2EF}
\definecolor{RubinTeal2}{HTML}{009FA1}
\definecolor{RubinTeal3}{HTML}{0C4A47}

% The complimentary grey colors
\definecolor{RubinGray0}{HTML}{DCE0E3}
\definecolor{RubinGray1}{HTML}{6A6E6E}
\definecolor{RubinGray2}{HTML}{1F2121}

% The  accent colors
\definecolor{RubinRed}{HTML}{ED4C4C}
\definecolor{RubinOrange}{HTML}{FAB364}
\definecolor{RubinYellow}{HTML}{FFE366}
\definecolor{RubinPurple}{HTML}{583671}
\definecolor{RubinGreen}{HTML}{3CAE3F}
\definecolor{RubinBlue}{HTML}{1C81A4}

% Shapes
\newcommand{\mysquare}[1][black]{\small\textcolor{#1}{\ensuremath\blacksquare}}
\newcommand{\mycirc}[1][black]{\Large\textcolor{#1}{\ensuremath\bullet}}
\newcommand{\dpcirc}[1][RubinDarkTeal]{\Large\textcolor{#1}{\ensuremath\bullet}}

% Local commands go here.

% Define common parameters
\newcommand{\currentdate}{November 2025}\xspace
\newcommand{\opsstartdate}{2025-10-25}\xspace
\newcommand{\ccfpdate}{2025-10-24}\xspace
\newcommand{\cstrcompdate}{2025-10-24}\xspace
\newcommand{\lcfpdate}{2025-04-15}\xspace
\newcommand{\rfldate}{2025-06-23}\xspace
\newcommand{\startsv}{2025-06-20}\xspace
\newcommand{\finonskylsstcam}{2025-09-21\xspace}\xspace
\newcommand{\startsciencelsstcam}{2025-04-17\xspace}\xspace
\newcommand{\startonskylsstcam}{2025-04-15\xspace}\xspace
\newcommand{\cameraontma}{2025-03-05\xspace}\xspace

\newcommand{\dpdd}{Data Products Definition Document (\DPDD{})\xspace}
\newcommand{\dpv}{Data Preview\,}\xspace
\newcommand{\dpvs}{Data Previews\,}\xspace
\newcommand{\dpzero}{Data Preview 0 (DP0)\,}\xspace
\newcommand{\dpone}{Data Preview 1 (DP1)\,}\xspace
\newcommand{\dptwo}{Data Preview 2 (DP2)\,}\xspace
\newcommand{\drone}{Data Release 1 (DR1)\,}\xspace
\newcommand{\tvssc}{Transients and Variable Stars Science Collaboration (TVSSC)\xspace}
\newcommand{\sssc}{Solar System Science Collaboration (SSSC)\xspace}
\newcommand{\diffim}{Difference Imaging\,}\xspace
\newcommand{\drp}{Data Release Production (DRP)\,}\xspace
\newcommand{\ap}{Alert Production (AP)\,}\xspace
\newcommand{\ro}{Rubin Observatory\xspace}
\newcommand{\rolsst}{Rubin Observatory Legacy Survey of Space and Time (LSST)\xspace}
\newcommand{\vrolsst}{Vera C. Rubin Observatory Legacy Survey of Space and Time (LSST)\xspace}
\newcommand{\lsst}{Legacy Survey of Space and Time (LSST)\xspace}
\newcommand{\svs}{Science Validation Surveys\xspace}
\newcommand{\sqdeg}{deg$^2$\xspace}

\newcommand{\TODO}[2]{\textcolor{red}{{TODO (#1): #2}}}

%If you want glossaries
%\input{aglossary.tex}
%\makeglossaries

\title{Rubin Observatory Plans for an Early Science Program}

% Optional subtitle
% \setDocSubtitle{A subtitle}

\author{%
Leanne~P.~Guy, Keith~Bechtol, Eric~Bellm, Bob~Blum, Gregory~P.~Dubois-Felsmann, Melissa~L.~Graham,
\v{Z}eljko~Ivezi\'{c}, R.~Lynne~Jones, Robert~H.~Lupton, Phil~Marshall, Colin~T.~Slater, Michael~Strauss.}

\setDocRef{RTN-011}
\setDocUpstreamLocation{\url{https://github.com/rubin-observatory/rtn-011}}

\date{\vcsDate}

% Optional: name of the document's curator
\setDocCurator{Leanne Guy}

% Leanne
\setDocAbstract{%

This document presents  Rubin Observatory’s plan for an \emph{Early Science Program} designed to enable high-impact science  prior to the first annual data release of the Legacy Survey of Space and Time (LSST).
The program includes the release of data products based on a reprocessing of science-grade commissioning data through a series of Data Previews, a progressive ramp-up of the transient alert stream beginning in the late commissioning phase, and an incremental template-generation strategy to support early alert production.
Additional components include the release of nightly Processed Visit Images (PVIs) and associated Source catalogs during the first 2 years of the survey, leading up to Data Release 1 (DR1), which will be based on the first year of LSST observations.
A detailed schedule of expected data products and milestones is provided.
Developed in close collaboration with the science community, this living plan will continue to evolve through the start of LSST operations and DR1 in response to early system performance and community feedback.
}


% Change history defined here.
% Order: oldest first.
% Fields: VERSION, DATE, DESCRIPTION, OWNER NAME.
% See LPM-51 for version number policy.
\setDocChangeRecord{%
  \addtohist{1}{2020-10-30}{First draft}{Leanne Guy}
  \addtohist{2}{2020-12-16}{Draft 1.1}{Bob Blum}
  \addtohist{3}{2021-10-08}{Rework structure}{Leanne Guy}
  \addtohist{4}{2021-10-21}{Add timeline}{Leanne Guy}
  \addtohist{5}{2021-11-05}{Edits throughout}{Eric Bellm}
  \addtohist{6}{2021-11-09}{Global edits and consolidation}{Leanne Guy}
  \addtohist{7}{2022-10-14}{Data Preview content, and incremental templates, revision of Early Science scenarios, address feedback from PCW 2022}{Phil Marshall \& Leanne Guy}
  \addtohist{8}{2022-10-21}{Release version 2.0}{Leanne Guy}
  \addtohist{9}{2022-10-24}{Changes to SCOC and survey text. Release version 2.1}{Leanne Guy}
  \addtohist{10}{2022-11-16}{Clarifications on alert production during commissioning. Release version 2.2}{Leanne Guy}
  \addtohist{11}{2023-01-10}{Updates following the construction project replan, refactoring of document to remove duplication.  Release version 3.}{Leanne Guy}
  \addtohist{12}{2023-01-12}{Correct Table 1 DP1 data products, Release version 3.1 }{Leanne Guy, Phil Marshall}
  \addtohist{13}{2023-06-01}{Updates following April schedule workshop; revision of early science scenarios; additional details on the data access environment}{Leanne Guy}
  \addtohist{14}{2023-06-21}{Release version 4.0}{Leanne Guy}
  \addtohist{15}{2023-10-31}{Updates following October schedule workshop}{Leanne Guy}
  \addtohist{16}{2023-10-31}{Release version 5.0}{Leanne Guy}
  \addtohist{17}{2024-05-02}{Added statement on non-sidereal tracking.}{Leanne Guy}
  \addtohist{18}{2024-05-03}{Release version 5.1}{Leanne Guy}
  \addtohist{19}{2025-02-10}{Major updates to the plans and data products for DP1. Revision of the Alert Production section. Release version 6.0}{Leanne Guy}
  \addtohist{20}{2025-02-24}{Minor updates to add more information on DP1 data products. Release version 6.1}{Leanne Guy}

  \addtohist{21}{2025-05-30}{Updates to DP1 data products, release timeline and moving object alert packet, Release version 6.2}{Melissa Graham, Leanne Guy, Eric Bellm}
 \addtohist{22}{2025-08-19}{Create Rubin DOI}{T. Jenness}
 \addtohist{23}{2025-11-07}{Updates to LSSTCam commissioning  release timeline.}{Leanne Guy, Eric Bellm, Lynne Jones. }
 \addtohist{24}{2025-11-10}{Release V7.0}{Leanne Guy}
}

% Optional set citation information
\setDocCitationInformation{
Leanne P. Guy, et al. Rubin Observatory Plans for an Early Science Program. NSF-DOE Vera C. Rubin Observatory RTN-011, \url{https://doi.org/10.71929/rubin/2584021}.}

\graphicspath{{./}{figures/}}
\setcounter{tocdepth}{2}

\begin{document}

% Create the title page.
\maketitle

% ADD CONTENT HERE
\input{intro}
\input{commissioning}
\input{datapreview}
\input{alertproduction}
\input{access}
\input{science}
\input{timeline}
\input{communication}

\appendix
% Include all the relevant bib files.
% https://lsst-texmf.lsst.io/lsstdoc.html#bibliographies
\section{References} \label{sec:bib}
\renewcommand{\refname}{} % Suppress default Bibliography section
\bibliography{local,lsst,lsst-dm,refs_ads,refs,books}

% Make sure lsst-texmf/bin/generateAcronyms.py is in your path
\section{Acronyms} \label{sec:acronyms}
\input{acronyms.tex}
% If you want glossary uncomment below -- comment out the two lines above
%\printglossaries

\end{document}
