\section{Roadmap and Timeline} \label{sec:timeline}

Table~\ref{tab:ops-timeline} shows the Operations timeline and provides nominal date ranges for the various elements of the Early Science Program.
The date ranges are derived from the Rubin ``Celebratory Milestones'', which are  published monthly on the Rubin Project website\footnote{\url{ls.st/dates}}. 
For completed milestones the delivered date is given. 
Milestone dates are given as min -- max ranges to indicate the associated uncertainty. 
Typically the near date corresponds to the current Project forecast, plus any additional operational uncertainty.
The late date corresponds approximately to the current Project late date plus any additional operational uncertainty.
The shaded region contains roughly 80\% of the probability, while the lefthand edge of the shaded range indicates the earliest date the milestone could be reached. 
The darker regions give a very rough indication of the +/-1 sigma error bars.
Over the course of the commissioning period, we expect these data ranges to shrink as our understanding of the remaining schedule uncertainty improves. 
However, there is still the possibility of the assumptions underlying these distributions being wrong; this is just our best estimate at the current time.

\input{tables/rubin_ops_timeline_simple}

The next key milestone in the Early Science Program is the release of DP1, expected sometime between October 2024 -- July 2025.
The  start of Rubin Operations is currently expected to be sometime between May 2025 and September 2025.
The timing of the Commissioning observations and their release to the community can only be projected to within a few months at the time of writing.
The late dates for the DP2 and DR1 milestones allow for the possibility that the Project completes within its late date, but in doing so spends less time on-sky with LSSTCam.
In this eventuality, the operations team would spend up to 2 months prior to commencing the 10-year LSST survey collecting more on-sky data to complement and extend the datasets collected during commissioning (see \S~\ref{ssec:scenarios}). 

Table ~\ref{tab:ops-timeline} will continue to be refined and updated in future version of this document as the Early Science Program progresses.